Analysis of Programming Students' Prompts to Identify Interactions Patterns with Generative AI

### 2024-09-24 CSEDU2025/Paper.tex
update

@@

@@

>>>>

% Since most of the messages are located in categories where students are 
% notoriously more active in their learning (conceptual questions 32.1% and 
% Debugging Help 30.9%), it seems that students are trying to use the AI in a 
% way that promotes their learning. However, the pattern of conversations with 
% sequential blocks and also little spacing may suggest that there is a gap in 
% knowledge of study strategies.

@@

To highlight the low incidence of interleaving, we conducted an analysis to
identify blocks of four or more consecutive messages classified within the same
category. The results showed that approximately 36\% of the messages are
distributed across 22 blocks. Specifically, the Debugging Help category contains
10 blocks of four or more messages, Conceptual Question has seven blocks,
Multiple Choice has three blocks, while Code Snippet and Complete Solution each
have one block.

Interestingly, when expanding the analysis to blocks of three consecutive
messages, the percentage of messages grouped within blocks of the same category
increases to about 45% of the total. It is also worth noting that three
categories – Student Correction, Language Change, and Uncategorized – did not
form any sequential blocks. The figure \ref{fig:graph2} shows 15 conversations,
one clear example of blocks can be observed in conversation eight which contains
two blocks of Multiple Choice questions. Another example is conversation 10,
with the entire conversation forming a one block of Conceptual Questions.

@@

% Another interesting study technique is spacing. Only 7.4% of the conversations
% exhibited message delays exceeding 24 hours and 26.19% involved response times 
% longer than 60 minutes. However, Carlos told me that this may be due to some 
% limitation of the bot, as it only maintains a conversation while the browser 
 % tab is open.

 % There is a big difference (I haven't looked at it statistically yet) in the 
%  interaction time with the Bot when a student asks conceptual questions. 
%  Perhaps this actually makes sense, since it is a category where, from the 
%  point of view of the metacognitive objective, the student is more concerned 
%  with understanding a concept and deeper learning.
